

# set up the python environment 

```{python}
import ee
import os
import geemap 
import geopandas as gpd
# earthengine calls 
ee.Initialize()
```

## define the initial parameters 

```{python}
# read in all gpd objects 
grid = gpd.read_file("C:/Users/carverd/Documents/GitHub/Agroforestry/testing/data/twelve_mi_grid_uid.gpkg")
ne = gpd.read_file("C:/Users/carverd/Documents/GitHub/Agroforestry/data/referenceData/nebraska_counties.gpkg")
points = gpd.read_file("C:/Users/carverd/Documents/GitHub/Agroforestry/testing/data/testSamplingData.geojson")
year = 2016
size = 30 
compactness = 0.1
connectivity = 8 
```


## define classification function
We'll need to have some code set up for selecting the specific reference data to use for now it's just hard coded
```{python}

def geePrint(feature):
  print(feature.getInfo());

def generateSNICData(year,aoi,size,compactness, connectivity):
  # convert to an ee object 
  sp1 = geemap.gdf_to_ee(aoi)
  
  # grab naip for area and year 
  naip1 = geemap.get_annual_NAIP(year).filterBounds(sp1).mosaic()  
  
  # generate NDVI 
  ndvi = naip1.normalizedDifference(["N","R"])
  
  # add ndvi to naip image 
  naip = naip1.addBands(ndvi)
  
  # run the segementation
  snic = ee.Algorithms.Image.Segmentation.SNIC(naip,size,compactness,connectivity)
  
  # select specific bands and combine with original image
  snicModel = snic.select('R_mean', 'G_mean', 'B_mean','N_mean', "nd_mean").addBands(naip);
  
  return snicModel


def applyRFModel(snicModel, rfmodel):
  # apply the model to the imagery 
  classified = snicModel.classify(rfmodel);
  return classified


def exportRFModel(downloadPath, classifiedImage,year,aoiSubNet):
  # Convert the aoi object to a GEE feature 
  sp_ee = geemap.gdf_to_ee(aoiSubNet)
  # grab the number of features to itorate over 
  size = sp_ee.size().getInfo()
  for i in range(size): # set to size when running
    print(i)
    # grab a subset of the area 
    sp2 = aoiSubNet.iloc[[i]]
    # convert to gee object for 
    sp_ee2 = geemap.gdf_to_ee(sp2).geometry()
    # filter the image 
    image = classifiedImage.clip(sp_ee2)
    # define file name 
    ### need to work on the download location path
    # filename = downloadPath + "/naip"+str(year)+"_" + str(i) + ".tif"
    filename = "naip"+str(year)+"_" + str(i) + ".tif"

    geemap.ee_export_image(
        image,
        filename=filename,
        scale = 1, # scale in meters probably best to call best on x,y of image rather then define.
        region=sp_ee2,
        file_per_band=False)
        ;
  




def generateRFModel(year,points,size,compactness, connectivity):
  # convert to an ee object 
  sp1 = geemap.gdf_to_ee(points)
  
  # map to show relative locations of features 
  # ax = aoi_pandas.plot(color="palegreen", edgecolor="green", figsize=(20, 10))
  # s.plot(ax=ax, color="red")
  # plt.show()
  # 
  
  # grab naip for area and year 
  naip1 = geemap.get_annual_NAIP(year).filterBounds(sp1).mosaic() # 
  # generate NDVI 
  ndvi = naip1.normalizedDifference(["N","R"])
  # add ndvi to naip image 
  naip = naip1.addBands(ndvi)
  
  
  # parameters for the segmentation process

  # run the segementation
  snic = ee.Algorithms.Image.Segmentation.SNIC(naip,size,compactness,connectivity)
  # select specific bands and combine with original image
  snicModel = snic.select('R_mean', 'G_mean', 'B_mean','N_mean', "nd_mean").addBands(naip)
  
  ## Extract values to points 
  extract_vals = snicModel.sampleRegions(collection=sp1, scale=1)
  # print(extract_vals.getInfo())
  # easiest print statement
  geemap.ee_to_gdf(extract_vals)
  

def generateRF(points,snicModel,nTrees):
  # convert to an ee object 
  sp1 = geemap.gdf_to_ee(points)
  #extract values to points 
  extract_vals = snicModel.sampleRegions(collection=sp1, scale=1)

  # generate a rf model 
  trainingclassifier = ee.Classifier.smileRandomForest(numberOfTrees = 10, seed = 7).train(features= extract_vals,classProperty = 'presence');
  
  return trainingclassifier

```

## run the classification function
```{python}
# generate the snic model based on the training dataset points 
snicModel = generateSNICData(year=year,aoi=points, size=size,compactness=compactness, connectivity=connectivity)

#produce the random forest model from the 
rfModel = generateRF(points=points, snicModel=snicModel, nTrees= 20)
```


## define R environment 
```{r}
pacman::p_load(sf,terra, dplyr,tmap)
tmap_mode("view")

#define AOI 
aoiID <- 'X12-695'
# this is not loading as a gpkg, saved as a geojson and moving on.. 
gridSF <- sf::st_read("C:/Users/carverd/Documents/GitHub/Agroforestry/testing/data/ne12Grid.geojson")

```

## define the sub grid AOI 
get the aoi and export a subgrid of 100 features(probably want to adjust the number of elements base on the download limit in GEE)
```{r}
source("~/GitHub/Agroforestry/testing/subsetAOI.R")
aoiSub <- subsetAOI(aoiID = aoiID, aoiSF = gridSF)
# Export the grided feature 
aoiSub |> 
  st_write("gridTemp.gpkg")

```


## Use grided features to project model and export results 

```{python}
# read in AOI element 
aoi = gpd.read_file("gridTemp.gpkg")
# generate a SNIC model 
snicAOI = generateSNICData(year=year,aoi=aoi, size=size,compactness=compactness,connectivity=connectivity )
# apply the rf model 
rfAOI = applyRFModel(snicModel=snicAOI,rfmodel=rfModel)
# export the model 
exportRFModel(classifiedImage=rfAOI,year=2016,aoiSubNet=aoi,downloadPath="NA")
### 20231106 -- classification took about 45 to download all files. This is not reasonable. Need to evaluated larger areas our different method etirely. 
```


## compare the classified elements against the existing layer 

```{r}
# merge all images back into a single object. 
allFeats <- list.files(pattern = ".tif",full.names = TRUE) |>
  purrr::map(rast) 

## this works but it is slow. 
for(i in seq_along(allFeats)){
  if(i == 1){
    r2 <- allFeats[[i]]
  }else{
    r2 <- terra::mosaic(x = r2, y = allFeats[[i]])
  }
}

```


```{r}
# convert the reference layer to a raster object 
ref1 <- "~/GitHub/Agroforestry/data/referenceData/Antelope_ALL_metrics_LCC_edited.shp"
sp2 <- terra::vect(ref1)
# create a raster object based on the dim of the shp file 

ras1 <- terra::rasterize(x = sp2)
```




