---
title: "R Notebook"
output: html_notebook
---

Authenticating GEE without gcloud installed 
earthengine authenticate --auth_mode=notebook in cmd
Same process as a notebook 



### Organized at the Collection Grid level

**inputs** : lat lon values from a relivent sampling location 

Gridded features from antelope county X12-601, X12-556, X12-510 

*model need to be developed outside of the applying step. Full unique workflow* 

1. Spilt the collection grid into smaller segements 

2. Pull naip imagery from earth engine for each segement (python)

3. merge and aggregate imagery to a scale that is approprate for the RF and segementation work 

4. generate indices uses in the modeling process 

5. generate a segmentation model 

## questions 
- not sure about the sequence of the segementation and RF modeling process 

- working exclusiveling in GEE might be a reasonable option as well. 



# environment setup 
```{r}
pacman::p_load(dplyr, terra, readr, sf, reticulate, raster, glcm)
source("~/Documents/Agroforestry/testing/subsetAOI.R")
source("~/Documents/Agroforestry/testing/aggregateImagery.R")
source("~/Documents/Agroforestry/testing/generateIndicies.R")
```

```{python}
import osgeo
import ee
import geemap
import geopandas as gpd
import torch
import samgeo 
# was getting a lot of library errors. I reinstalled via pip install -I rasterio
# import rasterio

# ee.Authenticate()
ee.Initialize()
```



read in files of interest and 
```{r}
grid <- st_read("~/Documents/Agroforestry/data/twelve_mi_grid_uid.gpkg")
aois <- grid$Unique_ID
# define aio
aoiID <- aois[100]

aoiSubGrid <- subsetAOI(aoiID = aoiID, aoiSF = grid)
# writing features seems like the best way to move objects between python and R tasks 
sf::st_write(aoiSubGrid, dsn = "~/Documents/Agroforestry/testing/subgrid.gpkg", delete_layer  = TRUE)


# seems a little weird to do it this way... might be able to just render directly as a python script 
## took about 10 minute to download an area. 
## 700ish areas * 3 time periods * 10 = 350 hours... 
source_python("downloadNAIP.py")

# loop over features to download 
downloadNAIP(aoi = "~/Documents/Agroforestry/testing/subgrid.gpkg",
             year = 2016,
             downloadPath = "testing/Downloads")
```




### 3. merge and aggregate imagery to a scale that is approprate for the RF and segementation work 

### 4. generate indices uses in the modeling process 
```{r}
r1 <- terra::rast("~/Documents/Agroforestry/testing/Downloads/naip2016_0.tif")
names(r1) <- c("r","g","b","n")
# 10 meter pixels for testing 
r2 <- ag(scaleFactor = 10, raster = r1)
r3 <- c(r2 , createNDVI(r2), createGLCM(band = r2[[4]],name = "nir"))
terra::writeRaster(r3 ,"~/Documents/Agroforestry/testing/Downloads/naip2016_0_indicies.tif")
```

### 5. generate a segmentation model 
```{python}
import os
import leafmap
import samgeo 


sam = SamGeo(
    model_type="vit_h",
    sam_kwargs=None,
)


```

